### 2012-08-28 paper_draft.tex
Now the abstract flows better

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
Genome-wide association studies are widely used to correlate phenotypic traits with genetic variants, for example Single Nucleotide Polymorphisms (SNPs). These studies compare the genetic variation between two groups to single out certain SNPs that are linked to a phenotypic variation in one of the groups. However, it is necessary to have a large enough sample size to find statistically significant correlations. The advent of Direct-To-Consumer genetic testing offers the analysis of SNPs for an individual at low cost without the need to consult a physician or geneticist. Over 100,000 people have already been genotyped through Direct-To-Consumer genetic testing companies. This data could be a valuable source for association studies. However, this data is not public for a variety of reasons and thus cannot be used in research. It seems reasonable to create a central open data-repository for such data, but it was previously unknown if and how people would submit their data to such a repository. Here we present a survey which evaluates whether people are willing to publicly share their genetic information. In the light of those results we present the web-platform openSNP, an open database which allows participants of Direct-To-Consumer genetic testing to publicly publish at no cost their genetic data along with phenotypic information. Through this "crowdsourced" effort of collecting genetic and phenotypic information openSNP has become a valuable resource which can be used in a wide array of studies, including Genome-wide association studies. OpenSNP is hosted at www.opensnp.org, and the code is released under MIT-license at github.com/gedankenstuecke/snpr

>>>>

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
Genome-wide association studies are widely used to correlate phenotypic traits with genetic variants. These studies usually compare the genetic variation between two groups to single out certain Single Nucleotide Polymorphisms (SNPs) that are linked to a phenotypic variation in one of the groups. However, it is necessary to have a large enough sample size to find statistically significant correlations. Direct-To-Consumer (DTC) genetic testing can supply additional data: DTC-companies offer the analysis of a large amount of SNPs for an individual at low cost without the need to consult a physician or geneticist. Over 100,000 people have already been genotyped through Direct-To-Consumer genetic testing companies. However, this data is not public for a variety of reasons and thus cannot be used in research. It seems reasonable to create a central open data-repository for such data, but it was previously unknown if and how people would submit their data to such a repository. Here we present a survey which evaluates whether people are willing to publicly share their genetic information. In the light of those results we present the web-platform openSNP, an open database which allows participants of Direct-To-Consumer genetic testing to publicly publish at no cost their genetic data along with phenotypic information. Through this "crowdsourced" effort of collecting genetic and phenotypic information openSNP has become a valuable resource which can be used in a wide area of studies, including Genome-wide association studies. OpenSNP is hosted at www.opensnp.org, and the code is released under MIT-license at github.com/gedankenstuecke/snpr
